Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-06-29 doc/ms.tex
Included updated measurements for time of first light in the paper.

To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
and the proportionality constant, and minimize $\chi^2$. 
The modeling results show that the SN flux rises approximately
linearly between
$t=-18\,\textrm{d}$ and $t=-14\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
the joint marginal distribution of $t_0$ and $\alpha$. From the
best-fit model we obtain $\alpha=0.98 \pm ^{0.06}_{0.10}$ and $t_0=-17.94 \pm ^{0.05}_{0.06}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
detection of \abc\ occurred $\sim{0.2}\,\textrm{d}$ after 
the SN first light. Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point. This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band. Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneous we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above. In the analysis that follows, the precise values of the best-fit parameters is not important. The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.

@@

\begin{figure*}[!thb]
  \centering
  \includegraphics[width=0.45\textwidth]{Chi2.pdf}
  \includegraphics[width=0.45\textwidth]{VelocityPlot.pdf}
  \caption{Constraints on $t_{exp}$ from fitting the velocity
    evolution of \ion{Si}{2}.
    \textit{Left panel:} the dashed, solid
    and dash-dotted curves show $\chi^2$ for fitting power laws with
    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
    vertical line and the orange shaded region indicate $t_0$ and its
    99.7\% confidence interval from Section
    \ref{sec:lc_fit}, respectively.
    \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
    velocities (blue circles) and the best-fit power-law model
     with an index of $-0.22$ (dashed line). Additionally the 
     measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
     are shown.}
  \label{fig:velocity_t_exp}
\end{figure*}

>>>>

To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$
and the proportionality constant, and minimize $\chi^2$. 
The modeling results show that the SN flux rises approximately
linearly between
$t=-18\,\textrm{d}$ and $t=-14\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
the joint marginal distribution of $t_0$ and $\alpha$. From the
best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$ and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
detection of \abc\ occurred $\sim{0.15}\,\textrm{d}$ after 
the SN first light. Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point. This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band. Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneous we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above. In the analysis that follows, the precise values of the best-fit parameters is not important. The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.

@@

\begin{figure*}[!thb]
  \centering
  \includegraphics[width=0.45\textwidth]{Chi2.pdf}
  \includegraphics[width=0.45\textwidth]{VelocityPlot.pdf}
  \caption{Constraints on $t_{exp}$ from fitting the velocity
    evolution of \ion{Si}{2}.
    \textit{Left panel:} the dashed, solid
    and dash-dotted curves show $\chi^2$ for fitting power laws with
    indices $-0.20$, $-0.22$ and $-0.24$, respectively. The blue
    vertical line and the orange shaded region indicate $t_0$ and its
    95\% confidence interval from Section
    \ref{sec:lc_fit}, respectively.
    \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
    velocities (blue circles) and the best-fit power-law model
     with an index of $-0.22$ (dashed line). Additionally the 
     measured velocites of \ion{C}{2}\,$\lambda\lambda$6580, 7234 
     are shown.}
  \label{fig:velocity_t_exp}
\end{figure*}
